Storm surge modelling in the Strait of Georgia

### 2014-11-21 RoughWork/manuscript.tex
Started text for Dec 2012

\subsection{High Resolution Atmospheric Forcing}

@@

\begin{figure}
\centering
\includegraphics[scale=0.6]{Figures/dec2012_weather.pdf}
\caption{Comparison of observed and modelled winds during Dec 2012 storm surge simulation at Point Atkinson and Sandheads.}
\label{fig:dec2013_weather}
\end{figure}

>>>>

\subsection{High Resolution Atmospheric Forcing}
The above comparison between the modelled and observed winds at Point Atkinson suggests that the atmopsheric forcing product (CGRF) may not be adequate to produce accurate storm surge hindcasts since the wind speeds are substanitially lower than observed. CGRF is a global atmospheric reforecasting model with horizontal resolution approximately 33 km over the Salish Sea domain, which is problematic since the Strait of Georgia itself is only about 30 km wide. As such, there are only one or two grid cells that are entirely over water in our domain, resulting in overly damped wind speeds at grid points close to land such as Point Atkinson. To determine the effect of underresolved wind forcing on the storm surge hindcasts we compare simulations that have been forced with 1) the low resolution CGRF model and 2) a high resolution operational model from Environment Canada.

%Where can I find a reference for the atmospheric model?

\begin{figure}
\centering
\includegraphics[scale=0.6]{Figures/dec2012_weather.pdf}
\caption{Comparison of observed and modelled winds during Dec 2012 storm surge simulation at Point Atkinson and Sandheads.}
\label{fig:dec2013_weather}
\end{figure}
%don't include direction?

@@
